A Large-scale Study of Polymorphism in R

### 2019-03-26 paper/main.tex
data and playing with plots

% latex table generated in R 3.5.1 by xtable 1.8-3 package
% Fri Mar 22 18:03:30 2019
\begin{table}[ht]
\label{tab:argcountsFGTS}
\centering
\begin{tabular}{rlrr}
  \hline
 & Argument Polymorphism & Count & Percentage \\ 
  \hline
  1 & Full Monomorphic & 784K & 85.19 \\ 
  2 & Monomorphic in Type & 839K & 91.27 \\ 
  3 & Monomorphic in Class & 831K & 90.31 \\ 
  4 & Monomorphic in Attribute Pattern & 830K & 90.25 \\ 
  5 & Total Seen & 920K & --- \\ 
     \hline
\end{tabular}
\caption{Account of {\it argument} polymorphism in the FGTS.}
\end{table}

% latex table generated in R 3.5.1 by xtable 1.8-3 package
% Fri Mar 22 18:10:46 2019
\begin{table}[ht]
\label{tab:funcountsFGTS}
\centering
\begin{tabular}{rlrr}
  \hline
 & Function Polymorphism & Count & Percentage \\ 
  \hline
  1 & Full Monomorphic & 143K & 65.64 \\ 
  2 & Monomorphic in Type & 169K & 77.65 \\ 
  3 & Monomorphic in Class & 163K & 75.13 \\ 
  4 & Monomorphic in Attribute Pattern & 161K & 74.31 \\ 
  5 & Total Seen & 217K & --- \\ 
   \hline
\end{tabular}
\caption{Account of {\it function} polymorphism in the FGTS.}
\end{table}

@@

The next type system design we will consider is ... .
\AT{Generate tables. The stuff we do is: real, NULL fold, NA fold.}

>>>>

% latex table generated in R 3.5.1 by xtable 1.8-3 package
% Fri Mar 22 18:03:30 2019
\begin{table}[ht]
\label{tab:argcountsFGTS}
\centering
\begin{tabular}{lrr}
  \hline
 Argument Polymorphism & Count & Percentage \\ 
  \hline
  Full Monomorphic & 784K & 85.19 \\ 
  Monomorphic in Type & 839K & 91.27 \\ 
  Monomorphic in Class & 831K & 90.31 \\ 
  Monomorphic in Attribute Pattern & 830K & 90.25 \\ 
  Total Seen & 920K & --- \\ 
     \hline
\end{tabular}
\caption{Account of {\it argument} polymorphism in the FGTS.}
\end{table}

% latex table generated in R 3.5.1 by xtable 1.8-3 package
% Fri Mar 22 18:10:46 2019
\begin{table}[ht]
\label{tab:funcountsFGTS}
\centering
\begin{tabular}{lrr}
  \hline
 Function Polymorphism & Count & Percentage \\ 
  \hline
  Full Monomorphic & 143K & 65.64 \\ 
  Monomorphic in Type & 169K & 77.65 \\ 
  Monomorphic in Class & 163K & 75.13 \\ 
  Monomorphic in Attribute Pattern & 161K & 74.31 \\ 
  Total Seen & 217K & --- \\ 
   \hline
\end{tabular}
\caption{Account of {\it function} polymorphism in the FGTS.}
\end{table}

@@

The next type system design we will consider is ... .

% latex table generated in R 3.5.1 by xtable 1.8-3 package
% Fri Mar 22 18:03:30 2019
\begin{table}[ht]
\label{tab:argcountsWHATTS}
\centering
\begin{tabular}{lrr}
  \hline
 Argument Polymorphism & Count & Percentage \\ 
  \hline
  Full Monomorphic & 785K & 85.38 \\ 
  Monomorphic in Type & 874K & 95.08 \\ 
%  Monomorphic in Class & 831K & 90.31 \\ 
%  Monomorphic in Attribute Pattern & 830K & 90.25 \\ 
  Total Seen & 920K & --- \\ 
     \hline
\end{tabular}
\caption{Account of {\it argument} polymorphism in the NEW TYPE SYSTEM.}
\end{table}

% latex table generated in R 3.5.1 by xtable 1.8-3 package
% Fri Mar 22 18:10:46 2019
\begin{table}[ht]
\label{tab:funcountsWHATTS}
\centering
\begin{tabular}{lrr}
  \hline
 Function Polymorphism & Count & Percentage \\ 
  \hline
  Full Monomorphic & 143K & 65.95 \\ 
  Monomorphic in Type & 186K & 85.85 \\ 
%  Monomorphic in Class & 163K & 75.13 \\ 
%  Monomorphic in Attribute Pattern & 161K & 74.31 \\ 
  Total Seen & 217K & --- \\ 
   \hline
\end{tabular}
\caption{Account of {\it function} polymorphism in the NEW TYPE SYSTEM.}
\end{table}

We had some big wins here.

How do the top signatures shake out now?
